Initial Analysis

### 2020-02-11 Initial_Analysis.Rmd
Comments to weighted method

@@

Global_Catch <- 108 # million (estimated from sau.com)

@@

label_data_rev <- Subregion_Data_Trans %>% 
  arrange(Total_USD_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )
  )

label_data_catch <- Subregion_Data_Trans %>% 
  arrange(fishing_entity_catch_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )
  )

@@

>>>>

# -------------------------- #
# Percentage of capture analyzed
# -------------------------- #

EEZ_Catch %>% 
  filter(
    reporting_status == "Reported",
    year > 2005) %>% 
  group_by(year) %>% 
  summarise(sum_year = sum(tonnes),
            sum_year_value = sum(landed_value)) %>% 
  group_by() %>% 
  summarise(mean(sum_year),
            mean(sum_year_value)
  )

Total_Catch_Spp <- 71842644/75202371

@@

Global_Catch <- 80 # million (estimated from sau.com)

@@

label_data_rev <- Subregion_Data_Trans %>% 
  arrange(Total_USD_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
  )

label_data_catch <- Subregion_Data_Trans %>% 
  arrange(fishing_entity_catch_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
  )

@@

```{r Territory_Map_Round_Weighted, eval =F, echo =F}
